---
title: "My first R Markdown script"
author: "Your name"
date: "This document was last modified on `r Sys.Date()`"
output: pdf_document
toc: yes
toc-depth: 4
---

# 1. Prepare to work

## 1.1 Set the working directory

Refer to Section 1.2 for this, Part 3.1.

## 1.2 Load the libraries

```{r}
#| warning: false
#| message: false
library(dplyr)
```

## 1.3 Load the data

```{r}
data <- read.csv("~/Fake/GACTT_RESULTS_ANONYMIZED_v2.csv", header=TRUE)
```

# 2. Preliminary observations and preparation of the data

## 2.1 Preliminary descriptive statistics

```{r}
## head(data, 5) ## Code not run because too lengthy
## str(data) ## Code not run because too lengthy
## summary(data) ## Code not run because too lengthy
```

## 2.2 Transformation of the data

### 2.2.1 Change of class

```{r}
data$What.is.your.age. <- as.factor(data$What.is.your.age.)
data$How.many.cups.of.coffee.do.you.typically.drink.per.day. <- as.factor(data$How.many.cups.of.coffee.do.you.typically.drink.per.day.)
data$Where.do.you.typically.drink.coffee. <- as.factor(data$Where.do.you.typically.drink.coffee.)
## summary(data) ## Code not run because too lengthy
```

```{r}
levels(data$What.is.your.age.)
levels(data$How.many.cups.of.coffee.do.you.typically.drink.per.day.)
levels(data$Where.do.you.typically.drink.coffee.)
```

### 2.2.2 Data selection

```{r}
data2 <- data[,c("Submission.ID",
                 "What.is.your.age.",
                 "How.many.cups.of.coffee.do.you.typically.drink.per.day.",
                 "Where.do.you.typically.drink.coffee.")] 
```

```{r}
data2 <- subset(data2, What.is.your.age. != "")
data2$What.is.your.age. <- droplevels(data2$What.is.your.age.)

data2 <- subset(data2, How.many.cups.of.coffee.do.you.typically.drink.per.day. != "")
data2$How.many.cups.of.coffee.do.you.typically.drink.per.day. <- droplevels(data2$How.many.cups.of.coffee.do.you.typically.drink.per.day.)
```

# 3. Summarize and plot the data

## 3.1 Create summary table

```{r}
data3 <- data2 %>% 
  group_by(What.is.your.age., How.many.cups.of.coffee.do.you.typically.drink.per.day.) %>% 
  summarize(Count = n())

data3
str(data3)
```

## 3.2 Change the order of the factors

```{r}
levels(data3$What.is.your.age.)
data3$What.is.your.age. <- factor(data3$What.is.your.age., levels = c("<18 years old",
                                                                      "18-24 years old",
                                                                      "25-34 years old",
                                                                      "35-44 years old",
                                                                      "45-54 years old",
                                                                      "55-64 years old",
                                                                      ">65 years old"))
levels(data3$What.is.your.age.)

levels(data3$How.many.cups.of.coffee.do.you.typically.drink.per.day.)
data3$How.many.cups.of.coffee.do.you.typically.drink.per.day. <- factor(data3$How.many.cups.of.coffee.do.you.typically.drink.per.day., levels = c("Less than 1",
                                                                      "1",
                                                                      "2",
                                                                      "3",
                                                                      "4",
                                                                      "More than 4"))
levels(data3$How.many.cups.of.coffee.do.you.typically.drink.per.day.)
```

## 3.3 Plot the data

```{r}
plot(x = data3$What.is.your.age., y = data3$Count)

```

```{r}
plot(x = data3$How.many.cups.of.coffee.do.you.typically.drink.per.day., y = data3$Count)
```

# 4. Save the data

## 4.1 Save as an R object

```{r}
save(data3, file = "data.Rdata")
```

## 4.2 Save as a CSV document

```{r}
write.csv(data3, "data3.csv", row.names = FALSE)
```
